### 2025-09-25 paper/sec/evaluation.tex
Purge obsolete content.

\section{Empirical Evaluation}
\label{sec:evaluation}

@@

\cdnote{I've bulked up the RQs qlthough I'm not sure we're actually attempting to answer them}
RQ1. How robust is the system when provided with incomplete or ambiguous information?
In real-world authoring tasks, text fragments may omit key criteria (e.g. \textbf{?}) or contain vague identifiers (e.g. \textbf{?} without further context).
We therefore ask how performance degrades when the specification is underspecified or when multiple interpretations are possible. Here, we distinguish between two forms of ambiguity:
(1) domain-level ambiguity, which reflects genuine uncertainty in the data (e.g. two models achieving identical scores).
(2) specification-level ambiguity, which arises from incomplete or imprecise descriptions in the query (e.g. missing fields that would otherwise resolve the expression uniquely).

@@

\begin{itemize}
\item How does performance degrade with partial/ambiguous information?
\item How is performance affected by ``adversarial'' (intentionally/unintentionally misleading) information?
\end{itemize}

Some ways we might explore these axes:
\begin{itemize}
\item meaningful vs.~meaningless vs.~misleading identifiers
\item leaving out key criteria (e.g.~year) that would resolve query to unique answer
\end{itemize}

We might want to distinguish ambiguity inherent in the problem domain (e.g.~uncertainty) vs.~ambiguity in the
specification of a particular code-generation query.

@@

    \centering
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD (\%)} & \textbf{Success Rate} & \textbf{SD (\%)} \\
            \hline
            Comparison     & 68.2   & 3.2 & 77.4 & 2 \\
            Data Retrieval & 77.3   & 3.7 & 77.4 & 2 \\
            Difference     & 20.0   & 44.7 & 77.4 & 2 \\
            Min/max        & 97.0   & 5.6 & 77.4 & 2 \\
            Rank           & 0.0   & 0.0 & 77.4 & 2 \\
            Sum            & 100   & 0.0 & 77.4 & 2 \\
            Ratio          & 100   & 0.0 & 77.4 & 2 \\
            Agerage        & 100   & 0.0 & 77.4 & 2 \\
            Overall        & 74.9 & 3 & 77.4 & 2 \\
            \hline
        \end{tabular}
        \caption{Results with target-value = true}
        \label{tab:results_true}
    \end{subtable}%
    \hfill
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD (\%)} & \textbf{Success Rate} & \textbf{SD (\%)} \\
            \hline
            Comparison     & 33.3 & 3.1 & -- & -- \\
            Data Retrieval & 62.0 & 1.6 & -- & -- \\
            Difference     & 75.0 & 50.0 & -- & -- \\
            Min/max        & 90.6 & 12.6 & -- & -- \\
            Rank           & 0.0 & 0.0 & -- & -- \\
            Sum            & 100.0 & 0.0 & -- & -- \\
            Ratio          & 100.0 & 0.0 & -- & -- \\
            Average        & 100.0 & 0.0 & -- & -- \\
            Overall        & 57.1 & 0.8 & -- & -- \\
            \hline
        \end{tabular}
        \caption{Results without target-value}
        \label{tab:results_no_target}
    \end{subtable}
    \caption{Comparison of success rates (with standard deviation) between \textbf{\gptfour} and \textbf{\gptfive} across different task categories, reported with and without the use of target-values.}
    \label{tab:results_combined}
\end{table}

>>>>

\section{Experimental Evaluation}
\label{sec:evaluation}

@@

RQ1. How robust is the system when provided with incomplete or ambiguous information?
In real-world authoring tasks, text fragments may omit key criteria (e.g. \textbf{?}) or contain vague identifiers (e.g. \textbf{?} without further context).
We therefore ask how performance degrades when the specification is underspecified or when multiple interpretations are possible. Here, we distinguish between two forms of ambiguity:
(1) domain-level ambiguity, which reflects genuine uncertainty in the data (e.g. two models achieving identical scores).
(2) specification-level ambiguity, which arises from incomplete or imprecise descriptions in the query (e.g. missing fields that would otherwise resolve the expression uniquely).

@@

@@

    \centering
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD (\%)} & \textbf{Success Rate} & \textbf{SD (\%)} \\
            \hline
            Comparison     & 68.2   & 3.2 & 77.4 & 2 \\
            Data Retrieval & 77.3   & 3.7 & 77.4 & 2 \\
            Difference     & 20.0   & 44.7 & 77.4 & 2 \\
            Min/max        & 97.0   & 5.6 & 77.4 & 2 \\
            Rank           & 0.0   & 0.0 & 77.4 & 2 \\
            Sum            & 100   & 0.0 & 77.4 & 2 \\
            Ratio          & 100   & 0.0 & 77.4 & 2 \\
            Agerage        & 100   & 0.0 & 77.4 & 2 \\
            Overall        & 74.9 & 3 & 77.4 & 2 \\
            \hline
        \end{tabular}
        \caption{Results with target-value = true}
        \label{tab:results_true}
    \end{subtable}%
    \hfill
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD (\%)} & \textbf{Success Rate} & \textbf{SD (\%)} \\
            \hline
            Comparison     & 33.3 & 3.1 & -- & -- \\
            Data Retrieval & 62.0 & 1.6 & -- & -- \\
            Difference     & 75.0 & 50.0 & -- & -- \\
            Min/max        & 90.6 & 12.6 & -- & -- \\
            Rank           & 0.0 & 0.0 & -- & -- \\
            Sum            & 100.0 & 0.0 & -- & -- \\
            Ratio          & 100.0 & 0.0 & -- & -- \\
            Average        & 100.0 & 0.0 & -- & -- \\
            Overall        & 57.1 & 0.8 & -- & -- \\
            \hline
        \end{tabular}
        \caption{Results without target-value}
        \label{tab:results_no_target}
    \end{subtable}
    \caption{Success rates (with standard deviation) for \textbf{\gptfour} and \textbf{\gptfive} across different task categories}
    \label{tab:results_combined}
\end{table}
